Object-based Auditory Scenes Similarity Retrieval and Classification With Scattering Transforms

### 2016-07-09 paper/structureScene.tex
add fig drafts for the ASS task using the test set

To compute the  weighted similarity between two scenes by taking into account both theirs clusters weights and theirs centroids similarities, we use a variant of the Earth Moving Distance ($EMD$) adapted for non-normalized histograms known as $\widehat{EMD}$ \cite{pele2008linear} with the implementation proposed in  \cite{pele2009fast}. Considering two histograms $h_i$ and $h_j$, represented the centroids weights of each scene, the $\widehat{EMD}$ is computed as follow:

@@

where $f_{ij}$ is the flow, and $D_{ij}$ is the ground distance. In our case the ground distance is $1-K^c_{ij}$

To get the final similarity measure between two scenes $s_i$ and $s_j$, we use an extended Gaussian kernels $K^s$ (Chapelle et al., 1999; Jing et al., 2003).

@@

with $A$ a scaling parameter, set to the mean value of the $\widehat{EMD}$. \\

The resulting kernel is an EMD kernel. It has to be noted that there is no proof that such kernel is positive definite.

>>>>

To compute the  weighted similarity between two scenes by taking into account both theirs clusters weights and theirs centroids similarities, we use a variant of the Earth Moving Distance ($EMD$) adapted for non-normalized histograms known as $\widehat{EMD}$ \cite{pele2008linear} with the implementation proposed in  \cite{pele2009fast}. Considering $h_i$ and $h_j$, the histograms of the centroids weights of the scenes $s_i$ and $s_j$ respectively, the $\widehat{EMD}$ is computed as follow:

@@

where $f_{ij}$ is the flow, and $D_{ij}$ is the ground distance. In our case, the ground distance is $D_{ij}=1-K^c_{ij}$.

To get the final similarity measure between two scenes $s_i$ and $s_j$, we use an extended Gaussian kernels $K^s$ \cite{chapelle1999support,jing2003support}.

@@

with $A$ a scaling parameter, set to the mean value of the $\widehat{EMD}$. The resulting kernel is called an EMD kernel, and it has to be noted that there is no proof that such kernel is positive definite. \\

Other articles using EMD in vision \cite{zhang2007local}
